Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-19 journal paper/content/conclusion.tex
fix typo in conclusion

\noindent One difficulty with the last two directions is that the bandit ``side" of the model becomes considerably more complicated, both in terms of the rewards and in terms of the algorithms. Indeed, there are many reasonable ways to model a changing world (resp., dependence on  contexts), and several  substantially different algorithmic approaches to deal \asedit{these models. Consequently, the distinctions between better and worse algorithms are not as clear and well-established.}

>>>>

\noindent One difficulty with the last two directions is that the bandit ``side" of the model becomes considerably more complicated, both in terms of the rewards and in terms of the algorithms. Indeed, there are many reasonable ways to model a changing world (resp., dependence on  contexts), and several substantially different algorithmic approaches to deal \asedit{with these models. Consequently, the distinctions between better and worse algorithms are not as clear and well-established.}
